Comparing Optimization Algorithms in the Fitting of Linear Mixed Models: Evaluating Speed and Accuracy using \pkg{lme4} in R and \pkg{lmm} in Julia

### 2015-08-27 inst/doc/Paper.Rnw
Reconfigured chunk float options, added more tables, general edits

\begin{table}[htbp]
\centering
\begin{tabular}{rllrrrrrr}
  \hline
 & opt & dsname & n & p & np & excess & time & reltime \\ 
  \hline
560 & NLOPT\_LN\_BOBYQA & Alfalfa &  72 &  12 &   1 & 0.00 & 0.04 & 27.52 \\ 
  561 & NLOPT\_LN\_BOBYQA & Animal &  20 &   1 &   2 & 0.00 & 0.02 & 13.92 \\ 
  562 & NLOPT\_LN\_BOBYQA & Assay &  60 &  31 &   2 & 0.00 & 0.03 & 10.80 \\ 
  563 & NLOPT\_LN\_BOBYQA & AvgDailyGain &  32 &   8 &   1 & 0.00 & 0.02 & 11.70 \\ 
  564 & NLOPT\_LN\_BOBYQA & AvgDailyGain &  32 &   5 &   1 & 0.00 & 0.02 & 13.70 \\ 
  565 & NLOPT\_LN\_BOBYQA & BIB &  24 &   8 &   1 & 0.00 & 0.02 & 12.61 \\ 
  566 & NLOPT\_LN\_BOBYQA & Bond &  21 &   3 &   1 & 0.00 & 0.02 & 23.27 \\ 
  567 & NLOPT\_LN\_BOBYQA & bs10 & 1104 &   4 &  20 & 0.00 & 4.66 & 18.88 \\ 
  568 & NLOPT\_LN\_BOBYQA & bs10 & 1104 &   4 &   8 & 0.00 & 1.06 & 15.65 \\ 
  569 & NLOPT\_LN\_BOBYQA & cake & 270 &  18 &   1 & 0.00 & 0.05 & 22.08 \\ 
  570 & NLOPT\_LN\_BOBYQA & Chem97 & 31022 &   1 &   2 & 0.00 & 0.63 & 3.94 \\ 
  571 & NLOPT\_LN\_BOBYQA & Chem97 & 31022 &   2 &   2 & 0.00 & 0.56 & 3.60 \\ 
  572 & NLOPT\_LN\_BOBYQA & Cultivation &  24 &   6 &   1 & 0.00 & 0.02 & 23.10 \\ 
  573 & NLOPT\_LN\_BOBYQA & d3 & 130418 &   2 &   9 & 0.00 & 231.30 & 2.16 \\ 
  574 & NLOPT\_LN\_BOBYQA & Demand &  77 &   5 &   2 & 0.00 & 0.03 & 3.81 \\ 
  575 & NLOPT\_LN\_BOBYQA & dialectNL & 225866 &   4 &   6 & 0.00 & 16.88 & 9.64 \\ 
  576 & NLOPT\_LN\_BOBYQA & Dyestuff2 &  30 &   1 &   1 & 0.00 & 0.05 & 62.58 \\ 
  577 & NLOPT\_LN\_BOBYQA & Dyestuff &  30 &   1 &   1 & 0.00 & 0.02 & 24.87 \\ 
  578 & NLOPT\_LN\_BOBYQA & egsingle & 7230 &   5 &   2 & 0.00 & 0.17 & 2.39 \\ 
  579 & NLOPT\_LN\_BOBYQA & ergoStool &  36 &   4 &   1 & 0.00 & 0.02 & 17.25 \\ 
  580 & NLOPT\_LN\_BOBYQA & Exam & 4059 &   5 &   1 & 0.00 & 0.05 & 5.40 \\ 
  581 & NLOPT\_LN\_BOBYQA & Exam & 4059 &   6 &   1 & 0.00 & 0.05 & 6.33 \\ 
  582 & NLOPT\_LN\_BOBYQA & Gasoline &  32 &   2 &   1 & 0.00 & 0.02 & 14.30 \\ 
  583 & NLOPT\_LN\_BOBYQA & gb12 & 512 &   8 &  20 & 0.00 & 1.87 & 9.28 \\ 
  584 & NLOPT\_LN\_BOBYQA & gb12 & 512 &   8 &   8 & 0.00 & 0.42 & 10.77 \\ 
  585 & NLOPT\_LN\_BOBYQA & Genetics &  60 &   5 &   2 & 0.00 & 0.03 & 9.60 \\ 
  586 & NLOPT\_LN\_BOBYQA & HR & 120 &   7 &   3 & 0.00 & 0.02 & 3.29 \\ 
  587 & NLOPT\_LN\_BOBYQA & Hsb82 & 7185 &   5 &   1 & 0.00 & 0.07 & 3.52 \\ 
  588 & NLOPT\_LN\_BOBYQA & IncBlk &  24 &   8 &   1 & 0.00 & 0.02 & 12.89 \\ 
  589 & NLOPT\_LN\_BOBYQA & InstEval & 73421 &  28 &   2 & 0.00 & 10.06 & 4.28 \\ 
  590 & NLOPT\_LN\_BOBYQA & InstEval & 73421 &   2 &   3 & 0.00 & 15.82 & 3.63 \\ 
  591 & NLOPT\_LN\_BOBYQA & kb07 & 1790 &   8 &  72 & 0.01 & 311.03 & 73.43 \\ 
  592 & NLOPT\_LN\_BOBYQA & kb07 & 1790 &   8 &  16 & 0.00 & 18.50 & 26.31 \\ 
  593 & NLOPT\_LN\_BOBYQA & Mississippi &  37 &   3 &   1 & 0.00 & 0.02 & 21.53 \\ 
  594 & NLOPT\_LN\_BOBYQA & mm0 & 69588 &   4 &   6 & 0.00 & 26.20 & 23.88 \\ 
  595 & NLOPT\_LN\_BOBYQA & Oxboys & 234 &   2 &   3 & 0.00 & 0.03 & 1.35 \\ 
  596 & NLOPT\_LN\_BOBYQA & Pastes &  60 &   1 &   2 & 0.00 & 0.02 & 9.51 \\ 
  597 & NLOPT\_LN\_BOBYQA & PBIB &  60 &  15 &   1 & 0.00 & 0.02 & 13.14 \\ 
  598 & NLOPT\_LN\_BOBYQA & Penicillin & 144 &   1 &   2 & 0.00 & 0.02 & 8.65 \\ 
  599 & NLOPT\_LN\_BOBYQA & Poems & 275996 &   3 &   3 & 0.00 & 21.31 & 3.74 \\ 
  600 & NLOPT\_LN\_BOBYQA & ScotsSec & 3435 &   4 &   2 & 0.00 & 0.08 & 5.04 \\ 
  601 & NLOPT\_LN\_BOBYQA & Semi2 &  72 &   2 &   3 & 0.00 & 0.03 & 9.27 \\ 
  602 & NLOPT\_LN\_BOBYQA & Semiconductor &  48 &  16 &   1 & 0.00 & 0.02 & 15.96 \\ 
  603 & NLOPT\_LN\_BOBYQA & SIMS & 3691 &   2 &   3 & 0.00 & 0.15 & 1.10 \\ 
  604 & NLOPT\_LN\_BOBYQA & sleepstudy & 180 &   2 &   3 & 0.00 & 0.04 & 5.30 \\ 
  605 & NLOPT\_LN\_BOBYQA & sleepstudy & 180 &   2 &   2 & 0.00 & 0.02 & 8.62 \\ 
  606 & NLOPT\_LN\_BOBYQA & TeachingII &  96 &  12 &   1 & 0.00 & 0.02 & 15.38 \\ 
  607 & NLOPT\_LN\_BOBYQA & Weights & 399 &   6 &   3 & 0.00 & 0.04 & 1.13 \\ 
  608 & NLOPT\_LN\_BOBYQA & WWheat &  60 &   2 &   3 & 0.00 & 0.03 & 2.32 \\ 
   \hline
\end{tabular}
\end{table}

\subsection[Convergence]{Proportion Converged}

The most important question regarding the optimizers is whether or not they have converged to the global optimum. We cannot test this directly. Instead we use a "crowd-sourced" criterion based on the minimum objective achieved by any of the algorithms. The difference between the objective achieved by a particular algorithm and this minimum is called the excess. In the summaries \texttt{excess} is rounded to 5 digits after the decimal so the minimum non-zero \texttt{excess} is $10^{-5}$.

@@

>>>>

\begin
{center}
<<results=tex,echo=FALSE>>=
print(xtable(subset(res, opt=="NLOPT_LN_BOBYQA")[1:8]), floating=FALSE, table.placement="H")
@
\end {center}

\subsection[Convergence]{Proportion Converged}
The most important question regarding the optimizers is whether or not they have converged to the global optimum. We cannot test this directly. Instead we use a "crowd-sourced" criterion based on the minimum objective achieved by any of the algorithms. The difference between the objective achieved by a particular algorithm and this minimum is called the excess. In the summaries \texttt{excess} is rounded to 5 digits after the decimal so the minimum non-zero \texttt{excess} is $10^{-5}$.

\begin
{center}
<<results=tex,echo=FALSE>>=
print(xtable(subset(res, opt=="LN_BOBYQA")[c(1,2,6)]),floating=FALSE, table.placement="H")
@
\end {center}

@@

<<results=tex>>=
print(xtable(subset(res, opt=="Nelder_Mead" & excess > 0.005)[c(1,2,3,5,6,7,8)]),floating=FALSE, table.placement="H")
@

<<results=tex>>=
print(xtable(subset(res, opt=="NLOPT_LN_Nelder_Mead" & excess > 0.005)[c(1,2,3,5,6,7,8)]),floating=FALSE, table.placement="H")
@

### 2015-08-27 inst/doc/Paper.tex
Used correct chunk options and fixed table float issue
Reconfigured chunk float options, added more tables, general edits

@@

\begin{table}[htbp]
\centering
\begin{tabular}{rllrrrrrr}
  \hline
 & opt & dsname & n & p & np & excess & time & reltime \\ 
  \hline
1 & LD\_CCSAQ & Alfalfa &  72 &  12 &   1 & 0.00 & 0.00 & 1.13 \\ 
  2 & LD\_CCSAQ & AvgDailyGain &  32 &   8 &   1 & 0.00 & 0.00 & 0.82 \\ 
  3 & LD\_CCSAQ & AvgDailyGain &  32 &   5 &   1 & 0.00 & 0.00 & 0.93 \\ 
  4 & LD\_CCSAQ & BIB &  24 &   8 &   1 & 0.00 & 0.00 & 0.79 \\ 
  5 & LD\_CCSAQ & Bond &  21 &   3 &   1 & 0.00 & 0.00 & 1.03 \\ 
  6 & LD\_CCSAQ & bs10 & 1104 &   4 &  20 & 0.00 & 1.10 & 4.44 \\ 
  7 & LD\_CCSAQ & bs10 & 1104 &   4 &   8 & 39.99 & 0.04 & 0.56 \\ 
  8 & LD\_CCSAQ & cake & 270 &  18 &   1 & 0.00 & 0.00 & 1.37 \\ 
  9 & LD\_CCSAQ & Cultivation &  24 &   6 &   1 & 0.00 & 0.00 & 0.99 \\ 
  10 & LD\_CCSAQ & Demand &  77 &   5 &   2 & 3.22 & 0.01 & 0.81 \\ 
  11 & LD\_CCSAQ & dialectNL & 225866 &   4 &   6 & 0.00 & 6.99 & 3.99 \\ 
  12 & LD\_CCSAQ & Dyestuff2 &  30 &   1 &   1 & 0.00 & 0.00 & 0.68 \\ 
  13 & LD\_CCSAQ & Dyestuff &  30 &   1 &   1 & 0.00 & 0.00 & 1.02 \\ 
  14 & LD\_CCSAQ & ergoStool &  36 &   4 &   1 & 0.00 & 0.00 & 1.10 \\ 
  15 & LD\_CCSAQ & Exam & 4059 &   5 &   1 & 0.00 & 0.01 & 1.19 \\ 
  16 & LD\_CCSAQ & Exam & 4059 &   6 &   1 & 0.00 & 0.01 & 1.32 \\ 
  17 & LD\_CCSAQ & Gasoline &  32 &   2 &   1 & 0.00 & 0.00 & 0.82 \\ 
  18 & LD\_CCSAQ & gb12 & 512 &   8 &  20 & 0.00 & 3.52 & 17.48 \\ 
  19 & LD\_CCSAQ & gb12 & 512 &   8 &   8 & 103.18 & 0.02 & 0.56 \\ 
  20 & LD\_CCSAQ & HR & 120 &   7 &   3 & 0.00 & 0.01 & 1.22 \\ 
  21 & LD\_CCSAQ & Hsb82 & 7185 &   5 &   1 & 192.73 & 0.01 & 0.49 \\ 
  22 & LD\_CCSAQ & IncBlk &  24 &   8 &   1 & 0.56 & 0.00 & 0.66 \\ 
  23 & LD\_CCSAQ & kb07 & 1790 &   8 &  72 & 8.21 & 17.47 & 4.12 \\ 
  24 & LD\_CCSAQ & Mississippi &  37 &   3 &   1 & 0.93 & 0.00 & 0.67 \\ 
  25 & LD\_CCSAQ & mm0 & 69588 &   4 &   6 & 0.00 & 4.83 & 4.40 \\ 
  26 & LD\_CCSAQ & Oxboys & 234 &   2 &   3 & 136.79 & 0.02 & 0.71 \\ 
  27 & LD\_CCSAQ & PBIB &  60 &  15 &   1 & 0.00 & 0.00 & 1.00 \\ 
  28 & LD\_CCSAQ & Penicillin & 144 &   1 &   2 & 0.00 & 0.01 & 4.94 \\ 
  29 & LD\_CCSAQ & Semiconductor &  48 &  16 &   1 & 0.00 & 0.00 & 1.05 \\ 
  30 & LD\_CCSAQ & SIMS & 3691 &   2 &   3 & 3.61 & 0.13 & 0.99 \\ 
  31 & LD\_CCSAQ & sleepstudy & 180 &   2 &   3 & 0.00 & 0.01 & 1.75 \\ 
  32 & LD\_CCSAQ & sleepstudy & 180 &   2 &   2 & 0.00 & 0.00 & 1.13 \\ 
  33 & LD\_CCSAQ & TeachingII &  96 &  12 &   1 & 0.00 & 0.00 & 0.93 \\ 
  34 & LD\_CCSAQ & Weights & 399 &   6 &   3 & 99.13 & 0.02 & 0.51 \\ 
  35 & LD\_CCSAQ & WWheat &  60 &   2 &   3 & 18.20 & 0.01 & 0.68 \\ 
   \hline
\end{tabular}
\end{table}

@@

\begin{table}[htbp]
\centering

@@

\end{tabular}
\end{table}

\subsection[Convergence]{Proportion Converged}

The most important question regarding the optimizers is whether or not they have converged to the global optimum. We cannot test this directly. Instead we use a "crowd-sourced" criterion based on the minimum objective achieved by any of the algorithms. The difference between the objective achieved by a particular algorithm and this minimum is called the excess. In the summaries \texttt{excess} is rounded to 5 digits after the decimal so the minimum non-zero \texttt{excess} is $10^{-5}$.

@@

>>>>

\begin{Schunk}
\begin{Sinput}
> load("~/Desktop/Summer_Sweave/Timings/data/res.rda")
\end{Sinput}
\end{Schunk}

@@

\begin
{center}
% latex table generated in R 3.1.3 by xtable 1.7-4 package
% Thu Aug 27 12:42:05 2015
\begin{table}[!htp]
\centering
\begin{tabular}{rllrrrrrr}
  \hline
 & opt & dsname & n & p & np & excess & time & reltime \\ 
  \hline
1 & LD\_CCSAQ & Alfalfa &  72 &  12 &   1 & 0.00 & 0.00 & 1.13 \\ 
  2 & LD\_CCSAQ & AvgDailyGain &  32 &   8 &   1 & 0.00 & 0.00 & 0.82 \\ 
  3 & LD\_CCSAQ & AvgDailyGain &  32 &   5 &   1 & 0.00 & 0.00 & 0.93 \\ 
  4 & LD\_CCSAQ & BIB &  24 &   8 &   1 & 0.00 & 0.00 & 0.79 \\ 
  5 & LD\_CCSAQ & Bond &  21 &   3 &   1 & 0.00 & 0.00 & 1.03 \\ 
  6 & LD\_CCSAQ & bs10 & 1104 &   4 &  20 & 0.00 & 1.10 & 4.44 \\ 
  7 & LD\_CCSAQ & bs10 & 1104 &   4 &   8 & 39.99 & 0.04 & 0.56 \\ 
  8 & LD\_CCSAQ & cake & 270 &  18 &   1 & 0.00 & 0.00 & 1.37 \\ 
  9 & LD\_CCSAQ & Cultivation &  24 &   6 &   1 & 0.00 & 0.00 & 0.99 \\ 
  10 & LD\_CCSAQ & Demand &  77 &   5 &   2 & 3.22 & 0.01 & 0.81 \\ 
  11 & LD\_CCSAQ & dialectNL & 225866 &   4 &   6 & 0.00 & 6.99 & 3.99 \\ 
  12 & LD\_CCSAQ & Dyestuff2 &  30 &   1 &   1 & 0.00 & 0.00 & 0.68 \\ 
  13 & LD\_CCSAQ & Dyestuff &  30 &   1 &   1 & 0.00 & 0.00 & 1.02 \\ 
  14 & LD\_CCSAQ & ergoStool &  36 &   4 &   1 & 0.00 & 0.00 & 1.10 \\ 
  15 & LD\_CCSAQ & Exam & 4059 &   5 &   1 & 0.00 & 0.01 & 1.19 \\ 
  16 & LD\_CCSAQ & Exam & 4059 &   6 &   1 & 0.00 & 0.01 & 1.32 \\ 
  17 & LD\_CCSAQ & Gasoline &  32 &   2 &   1 & 0.00 & 0.00 & 0.82 \\ 
  18 & LD\_CCSAQ & gb12 & 512 &   8 &  20 & 0.00 & 3.52 & 17.48 \\ 
  19 & LD\_CCSAQ & gb12 & 512 &   8 &   8 & 103.18 & 0.02 & 0.56 \\ 
  20 & LD\_CCSAQ & HR & 120 &   7 &   3 & 0.00 & 0.01 & 1.22 \\ 
  21 & LD\_CCSAQ & Hsb82 & 7185 &   5 &   1 & 192.73 & 0.01 & 0.49 \\ 
  22 & LD\_CCSAQ & IncBlk &  24 &   8 &   1 & 0.56 & 0.00 & 0.66 \\ 
  23 & LD\_CCSAQ & kb07 & 1790 &   8 &  72 & 8.21 & 17.47 & 4.12 \\ 
  24 & LD\_CCSAQ & Mississippi &  37 &   3 &   1 & 0.93 & 0.00 & 0.67 \\ 
  25 & LD\_CCSAQ & mm0 & 69588 &   4 &   6 & 0.00 & 4.83 & 4.40 \\ 
  26 & LD\_CCSAQ & Oxboys & 234 &   2 &   3 & 136.79 & 0.02 & 0.71 \\ 
  27 & LD\_CCSAQ & PBIB &  60 &  15 &   1 & 0.00 & 0.00 & 1.00 \\ 
  28 & LD\_CCSAQ & Penicillin & 144 &   1 &   2 & 0.00 & 0.01 & 4.94 \\ 
  29 & LD\_CCSAQ & Semiconductor &  48 &  16 &   1 & 0.00 & 0.00 & 1.05 \\ 
  30 & LD\_CCSAQ & SIMS & 3691 &   2 &   3 & 3.61 & 0.13 & 0.99 \\ 
  31 & LD\_CCSAQ & sleepstudy & 180 &   2 &   3 & 0.00 & 0.01 & 1.75 \\ 
  32 & LD\_CCSAQ & sleepstudy & 180 &   2 &   2 & 0.00 & 0.00 & 1.13 \\ 
  33 & LD\_CCSAQ & TeachingII &  96 &  12 &   1 & 0.00 & 0.00 & 0.93 \\ 
  34 & LD\_CCSAQ & Weights & 399 &   6 &   3 & 99.13 & 0.02 & 0.51 \\ 
  35 & LD\_CCSAQ & WWheat &  60 &   2 &   3 & 18.20 & 0.01 & 0.68 \\ 
   \hline
\end{tabular}
\end{table}\end {center}

@@

\begin
{center}
% latex table generated in R 3.1.3 by xtable 1.7-4 package
% Thu Aug 27 12:42:05 2015

@@

\end{tabular}\end {center}

\subsection[Convergence]{Proportion Converged}
The most important question regarding the optimizers is whether or not they have converged to the global optimum. We cannot test this directly. Instead we use a "crowd-sourced" criterion based on the minimum objective achieved by any of the algorithms. The difference between the objective achieved by a particular algorithm and this minimum is called the excess. In the summaries \texttt{excess} is rounded to 5 digits after the decimal so the minimum non-zero \texttt{excess} is $10^{-5}$.

\begin
{center}
% latex table generated in R 3.1.3 by xtable 1.7-4 package
% Thu Aug 27 12:42:05 2015
\begin{tabular}{rllr}
  \hline
 & opt & dsname & excess \\ 
  \hline
347 & LN\_BOBYQA & Alfalfa & 0.00 \\ 
  348 & LN\_BOBYQA & Animal & 0.00 \\ 
  349 & LN\_BOBYQA & Assay & 0.00 \\ 
  350 & LN\_BOBYQA & AvgDailyGain & 0.00 \\ 
  351 & LN\_BOBYQA & AvgDailyGain & 0.00 \\ 
  352 & LN\_BOBYQA & BIB & 0.00 \\ 
  353 & LN\_BOBYQA & Bond & 0.00 \\ 
  354 & LN\_BOBYQA & bs10 & 0.00 \\ 
  355 & LN\_BOBYQA & bs10 & 0.00 \\ 
  356 & LN\_BOBYQA & cake & 0.00 \\ 
  357 & LN\_BOBYQA & Chem97 & 0.00 \\ 
  358 & LN\_BOBYQA & Chem97 & 0.00 \\ 
  359 & LN\_BOBYQA & Cultivation & 0.00 \\ 
  360 & LN\_BOBYQA & d3 & 0.00 \\ 
  361 & LN\_BOBYQA & Demand & 0.00 \\ 
  362 & LN\_BOBYQA & dialectNL & 0.00 \\ 
  363 & LN\_BOBYQA & Dyestuff2 & 0.00 \\ 
  364 & LN\_BOBYQA & Dyestuff & 0.00 \\ 
  365 & LN\_BOBYQA & egsingle & 0.00 \\ 
  366 & LN\_BOBYQA & ergoStool & 0.00 \\ 
  367 & LN\_BOBYQA & Exam & 0.00 \\ 
  368 & LN\_BOBYQA & Exam & 0.00 \\ 
  369 & LN\_BOBYQA & Gasoline & 0.00 \\ 
  370 & LN\_BOBYQA & gb12 & 0.00 \\ 
  371 & LN\_BOBYQA & gb12 & 0.00 \\ 
  372 & LN\_BOBYQA & Genetics & 0.00 \\ 
  373 & LN\_BOBYQA & HR & 0.00 \\ 
  374 & LN\_BOBYQA & Hsb82 & 0.00 \\ 
  375 & LN\_BOBYQA & IncBlk & 0.00 \\ 
  376 & LN\_BOBYQA & InstEval & 0.00 \\ 
  377 & LN\_BOBYQA & InstEval & 0.00 \\ 
  378 & LN\_BOBYQA & kb07 & 0.02 \\ 
  379 & LN\_BOBYQA & kb07 & 0.00 \\ 
  380 & LN\_BOBYQA & Mississippi & 0.00 \\ 
  381 & LN\_BOBYQA & mm0 & 0.00 \\ 
  382 & LN\_BOBYQA & Oxboys & 0.00 \\ 
  383 & LN\_BOBYQA & Pastes & 0.00 \\ 
  384 & LN\_BOBYQA & PBIB & 0.00 \\ 
  385 & LN\_BOBYQA & Penicillin & 0.00 \\ 
  386 & LN\_BOBYQA & Poems & 0.00 \\ 
  387 & LN\_BOBYQA & ScotsSec & 0.00 \\ 
  388 & LN\_BOBYQA & Semi2 & 0.00 \\ 
  389 & LN\_BOBYQA & Semiconductor & 0.00 \\ 
  390 & LN\_BOBYQA & SIMS & 0.00 \\ 
  391 & LN\_BOBYQA & sleepstudy & 0.00 \\ 
  392 & LN\_BOBYQA & sleepstudy & 0.00 \\ 
  393 & LN\_BOBYQA & TeachingII & 0.00 \\ 
  394 & LN\_BOBYQA & Weights & 0.00 \\ 
  395 & LN\_BOBYQA & WWheat & 0.00 \\ 
   \hline
\end{tabular}\end {center}

@@

\begin{Schunk}
\begin{Sinput}
> print(xtable(subset(res, opt=="Nelder_Mead" & excess > 0.005)[c(1,2,3,5,6,7,8)]),floating=FALSE, table.placement="H")
\end{Sinput}
% latex table generated in R 3.1.3 by xtable 1.7-4 package
% Thu Aug 27 12:42:05 2015
\begin{tabular}{rllrrrrr}
  \hline
 & opt & dsname & n & np & excess & time & reltime \\ 
  \hline
777 & Nelder\_Mead & bs10 & 1104 &  20 & 71.39 & 145.37 & 588.68 \\ 
  783 & Nelder\_Mead & d3 & 130418 &   9 & 317.59 & 454.52 & 4.25 \\ 
  785 & Nelder\_Mead & dialectNL & 225866 &   6 & 181.63 & 54.54 & 31.16 \\ 
  793 & Nelder\_Mead & gb12 & 512 &  20 & 78.71 & 38.21 & 189.60 \\ 
  801 & Nelder\_Mead & kb07 & 1790 &  72 & 398.73 & 2825.46 & 667.02 \\ 
  802 & Nelder\_Mead & kb07 & 1790 &  16 & 403.48 & 269.44 & 383.09 \\ 
  803 & Nelder\_Mead & Mississippi &  37 &   1 & 0.04 & 0.02 & 20.40 \\ 
  804 & Nelder\_Mead & mm0 & 69588 &   6 & 181.63 & 76.87 & 70.07 \\ 
   \hline
\end{tabular}\end{Schunk}
